---
title: "Draft Quarto document"
author: "Alexander Hinz"
format: html
---

## Header 1

```{r setup}
#| include: false
library(tidyverse)
library(here)
library(snakecase)
```

```{r}
# Code chunk
```

## Importing CGM data
By removing () from to_snake_case we can apply the effects of the function to other functions.
Currently this reads to_snake_case as an object.
read_csv() is a function. to_snake_case() is a function. to_snake_case is not a function, but an object. The properties of the object can then be integrated into other functions. 
```{r}
cgm_101 <- here("data-raw/dime/cgm/101.csv") |>
  read_csv(
    show_col_types = FALSE,
    name_repair = to_snake_case,
    n_max = 100
  )

sleep_101 <- here("data-raw/dime/sleep/101.csv") |>
  read_csv(
    show_col_types = FALSE,
    name_repair = to_snake_case,
    n_max = 100
  )
sleep_101
```

## Making a function that add numbers together
```{r}
#' Add two numbers together
#'
#' @param num1 A number
#' @param num2 A number
#'
#' @returns Returns the sum of the numbers
#'
add_numbers <- function(num1, num2) {
  added <- num1 + num2
  return(added)
}

add_numbers(1, 2)
```

## Importing 101's cgm data with a function
```{r}
#' Import one cgm participant
#'
#' @param file_path Path to the file we want to open
#'
#' @returns Returns a dataframe
#'
Import_cgm <- function(file_path) {
  cgm <- file_path |>
    read_csv(
      show_col_types = FALSE,
      name_repair = snakecase::to_snake_case,
      n_max = 100
    )
  return(cgm)
}

here("data-raw/dime/cgm/101.csv") |>
  Import_cgm()

here("data-raw/dime/cgm/102.csv") |>
  Import_cgm()
```

## Importing 101's sleep data with a function 
```{r}
#' Import one sleep participant data
#'
#' @param file_path Path to the file we want to import
#'
#' @returns Returns a dataframe
#'
Import_sleep <- function(file_path) {
  sleep <- file_path |>
    readr::read_csv(
      show_col_types = FALSE,
      name_repair = to_snake_case,
      n_max = 100
    )
  return(sleep)
}

here("data-raw/dime/sleep/101.csv") |>
  Import_sleep()

here("data-raw/dime/sleep/101.csv") |>
  Import_sleep()
```

## Import DIME data function
```{r}
#' Importing data from DIME dataset
#'
#' @param file_path Path to the CSV file
#'
#' @returns Returns a dataframe
#'
import_dime <- function(file_path) {
  data <- file_path |>
    readr::read_csv(
      show_col_types = FALSE,
      name_repair = snakecase::to_snake_case,
      n_max = 100
    )

  return(data)
}
```

```{r}
here("data-raw/dime/cgm/101.csv") |>
  import_dime()

here("data-raw/dime/sleep/101.csv") |>
  import_dime()
```
