---
title: "Draft Quarto document"
author: "Alexander Hinz"
format: html
---

## Header 1

```{r setup}
#| include: false
library(tidyverse)
library(here)
library(snakecase)
library(fs)
library(lubridate)
library(stringr)
source(here("R/functions.R"))

cgm_data <- here("data-raw/dime/cgm/") |>
  import_csv_files() |>
  clean_cgm()

sleep_data <- here("data-raw/dime/sleep/") |>
  import_csv_files() |>
  get_participant_id() |>
  rename(datetime = date) |>
  prepared_dates(datetime)
```

```{r}
# Code chunk
```

## Importing CGM data

By removing () from to_snake_case we can apply the effects of the function to other functions. Currently this reads to_snake_case as an object. read_csv() is a function. to_snake_case() is a function. to_snake_case is not a function, but an object. The properties of the object can then be integrated into other functions.

```{r}
cgm_101 <- here("data-raw/dime/cgm/101.csv") |>
  read_csv(
    show_col_types = FALSE,
    name_repair = to_snake_case,
    n_max = 100
  )

sleep_101 <- here("data-raw/dime/sleep/101.csv") |>
  read_csv(
    show_col_types = FALSE,
    name_repair = to_snake_case,
    n_max = 100
  )
sleep_101
```

## Making a function that add numbers together

```{r}
#' Add two numbers together
#'
#' @param num1 A number
#' @param num2 A number
#'
#' @returns Returns the sum of the numbers
#'
add_numbers <- function(num1, num2) {
  added <- num1 + num2
  return(added)
}

add_numbers(1, 2)
```

## Importing 101's cgm data with a function

```{r}
#' Import one cgm participant
#'
#' @param file_path Path to the file we want to open
#'
#' @returns Returns a dataframe
#'
Import_cgm <- function(file_path) {
  cgm <- file_path |>
    read_csv(
      show_col_types = FALSE,
      name_repair = snakecase::to_snake_case,
      n_max = 100
    )
  return(cgm)
}

here("data-raw/dime/cgm/101.csv") |>
  Import_cgm()

here("data-raw/dime/cgm/102.csv") |>
  Import_cgm()
```

## Importing 101's sleep data with a function

```{r}
#' Import one sleep participant data
#'
#' @param file_path Path to the file we want to import
#'
#' @returns Returns a dataframe
#'
Import_sleep <- function(file_path) {
  sleep <- file_path |>
    readr::read_csv(
      show_col_types = FALSE,
      name_repair = to_snake_case,
      n_max = 100
    )
  return(sleep)
}

here("data-raw/dime/sleep/101.csv") |>
  Import_sleep()

here("data-raw/dime/sleep/101.csv") |>
  Import_sleep()
```

## Import DIME data function

```{r}
here("data-raw/dime/cgm/101.csv") |>
  import_dime()

here("data-raw/dime/sleep/101.csv") |>
  import_dime()
```

## Importing sleep data using map()

```{r}
sleep_files <- here("data-raw/dime/sleep/") |>
  dir_ls(glob = "*.csv")

sleep_files

sleep_data <- sleep_files |>
  map(import_dime) |>
  list_rbind(names_to = "file_path_id")

sleep_data
```

```{r}
here("data-raw/dime/cgm/") |>
  import_csv_files()
here("data-raw/dime/sleep/") |>
  import_csv_files()
```

## Summarising with across()

```{r}
cgm_data |>
  summarise(across(glucose, list(mean = mean, sd = sd, median = median)))
```

## Summarizing by groups

```{r}
cgm_data |>
  select(-contains("timestamp"), -contains("datetime")) |>
  group_by(pick(-glucose)) |>
  summarize(across(glucose, list(mean = mean, sd = sd)),
    .groups = "drop"
  )
```
